Realistically Interesting Domains for Probabilistic Planners

### 2014-04-08 FinalPaper/paper.tex
Glutton herschreven

\subsection{\textsc{Glutton}}

\textsc{Glutton} introduces an off-line algorithm based on LR$^2$TDP. The \emph{Max-Reward} heuristic used to evaluate \todo{the what?} relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it. In addition to LR$^2$TDP, it introduces the following mechanisms to optimize for large branching factors:

\todo{rewrite this list}

\myworries{is this really necessary?}

\begin{itemize}
	\item Sub sampling the transition function, is not enough to decrease the amount of computations yet
	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
	\item Caching the transition function samples: as LR$^2$TDP populates the state-value hash table lazily, \textsc{Glutton} uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair. When full, it chooses state-action pars for eviction ans replacement randomly.
	\item Default policies: \textsc{Glutton} uses 3 tricks to determine a policy when stopped prematurely. It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
\end{itemize}

%---------------------------------------------------------------------
%During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT. This caused to wonder whether LRTDP planners could outperform UCT based systems.  UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states. Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity. At the IPPC-11 \textsc{Glutton} was an offline LRTDP based planner that came second. As PROST employed UCT in an online manner, \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} algorithm to test whether LRTDP performs better if it is employed online.
%
%UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past. This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.

Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime. Such problems are far better solved using online planners by finding an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state, executing it and repeating. This is done by choosing a certain lookahead value $L$ and solving the MDP $M_s(L)$ to solve $M_0(H)$ where L $<$ H and then select $\pi^*_L(s,L)$ using the evaluation criteria. This lookahead value is determined using the per-process time constraint.

\todo{elaborate on the per-process time constraint}

>>>>

\subsection{\textsc{GLUTTON}}
The \textsc{GLUTTON} planner enhances LR$^2$TDP to cope with large branching factors by using several optimization techniques. It employs LR$^2$TDP in an off-line fashion by initializing the algorithm with the \emph{Max-Reward} heuristic that places an upper bound on the optimal value function $V^*$. It optimizes for large branching factors by performing the transition function in a subset of transition states $s'$. It distinguished between \emph{exogenous} effects caused by natural dynamics and \emph{pure} effects caused by the action itself and a mixed of both. It also utilized the saved memory space caused by mapping only the converged states in the hash-table by using the free space as cache for storing successor states computed using the transition function. 
Since \textsc{GLUTTON} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling. To compensate for these states, \textsc{GLUTTON} has to resort to a \emph{default policy}. \todo{Wel of niet de default policy uitleggen}.
%---------------------------------------------------------------------
%During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT. This caused to wonder whether LRTDP planners could outperform UCT based systems.  UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states. Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity. At the IPPC-11 \textsc{Glutton} was an offline LRTDP based planner that came second. As PROST employed UCT in an online manner, \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} algorithm to test whether LRTDP performs better if it is employed online.
%
%UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past. This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.

When however dealing with large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime. Such problems are far better solved using online planners that find an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state. 
%This is done by choosing a certain lookahead value $L$ and solving the MDP $M_s(L)$ to solve $M_0(H)$ where L $<$ H and then select $\pi^*_L(s,L)$ using the evaluation criteria. This lookahead value is determined using the per-process time constraint.
